Untrusted B2B Collaboration using the Blockchain

### 2018-07-23 paper/paper.tex
more future work

@@

>>>>

During evaluation, we saw that the instantiation costs are very high, have a potential to hit the gas limit in larger choreographies and also have to be paid by the initiator.
These problems need to be addressed before our solution is viable for production use.
One possbile way to distribute the costs among the participants makes use of triggers on the factory contracts.
Instead of creating all instance contracts transitively, the factory contract would have a method for accepting requests for instantiation.
The process engine could then react to such a call via a trigger, and call the instantiation method.
Then the other factory would have to be notified that the instantiation was successful.

@@

Currently all contracts are written manually.
Since the contracts all share the same patterns,  this is a prime candidate for automation.
A possible implementation could use a rule-based approach for translating the choreography model, similar to \cite{lopez2017caterpillar}.
This would then automatically generate Solidity code for the access and factory contracts.
